### 2016-09-01 RA-L/experiment.tex
moved files

\begin{figure*}[!htb]
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{
\begin{overpic}[width =\figwid]{twoR1.pdf}\put(12,70){$t$  = 0 s}\end{overpic}
\begin{overpic}[width =\figwid]{twoR2.pdf}\put(12,70){$t$  = 60 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR3.pdf}\put(12,70){$t$  = 150 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR4.pdf}\put(12,70){$t$  = 160 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR5.pdf}\put(12,70){$t$  = 210 s}
\end{overpic}}
\vspace{-3em}
\caption{\label{fig:storyReal}{Positioning of two kilobots where they should reach their same color circle. The boundary walls have nearly infinite friction, so the green robot is stopped by the wall from $t = 60$s until the commanded input is directed away form the wall at $t=150$s, while the pink robot in free-space is unhindered.}
%\vspace{-1em}
}
\end{figure*}

>>>>

\begin{figure*}[!htb]
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{
\begin{overpic}[width =\figwid]{twoR1.pdf}\put(12,70){$t$  = 0 s}\end{overpic}
\begin{overpic}[width =\figwid]{twoR2.pdf}\put(12,70){$t$  = 60 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR3.pdf}\put(12,70){$t$  = 150 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR4.pdf}\put(12,70){$t$  = 160 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR5.pdf}\put(12,70){$t$  = 210 s}
\end{overpic}}
\vspace{-3em}
\caption{\label{fig:storyReal}{
Position control of two kilobots (Alg. \ref{alg:XControl}) steered to corresponding colored circle. Boundary walls have nearly infinite friction, so the green robot is stopped by the wall from $t = 60$s until the commanded input is directed away form the wall at $t=150$s, while the pink robot in free-space is unhindered.}
%\vspace{-1em}
}
\end{figure*}
